Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-12 papers/histogram/sad.tex
some more data, and add more caption information to sad.tex

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv-error}
  \caption{The maximum error in the heat capacity of the LJ31 cluster
    in the temperature range from 0.01~$\epsilon/k_B$ to
    0.1~$\epsilon/k_B$.}
  \label{fig:lj-cv-error}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv-error}
  \caption{The maximum error in the heat capacity of the LJ31 cluster
    in the temperature range from 0.01~$\epsilon/k_B$ to
    0.1~$\epsilon/k_B$.  Note that the value of $C_V$ ranges from
    90$k_B$ to 120$k_B$, so the smallest (maximum) errors seen are
    around 1\%.  All WL methods shown were run with a histogram bin
    width of $\Delta E=0.01\epsilon$.  Their convergence at other bin
    widths was similar to that of SAD. }
  \label{fig:lj-cv-error}
\end{figure}
